Gozde and Liora extension

### 2015-04-27 extension.Rmd
Extension final version

---
title: "Gozde and Liora extension"
author: "Liora Goldensher"
date: "April 27, 2015"
output:
  html_document:
    pandoc_args: [
      "+RTS", "-K64m",
      "-RTS"
    ]
---
# EXTENSION

@@

```{r}
library(separationplot)
library(Hmisc) 
library(zoom)

@@

log.odds <- model_1$fitted.values # Create a vector with log-odd values
# Create link function to transform log-odds into predicted probabilities
link <- function(P) {
  1/(1+exp(-P))
} 
pred <- link(log.odds) # Transform log-odds into predicted probabilities
pred <- as.vector(pred) 
range(pred) # variation in the predicted probabilities: very little variation.
dev.off()
# Create separation plot to visualize the predictive power of the model
plot_model1 <- separationplot(pred = pred, actual = actual, type = "rect", heading = "Model1: The Adorno Thesis", xlab = "ER Vote Intention", newplot = F, line = T, lwd2 = 0.8, height = 0.5, show.expected = T) 
```

@@

# Model 2: Parsons Thesis (Social Disintegration)
Parsons' 1942 theory of social disintegration posits that anomia, a breakdown of social norms, and attendant feelings of anxiety, anger and isolation brings about a longing for strong leadership and rigid ideologies that extreme right parties can provide.  While we do not have measures for the emotions of participants in the studies whose data we use, in our second model we examine the relationship between extreme right voting and the kinds of sentiments about social change that Parsons refers to: satisfaction with democracy and the negative evaluation of the European Union.

@@

log.odds <- model_2$fitted.values # Create a function with log-odds
# Create link function to transform log-odds into predicted probabilities
link <- function(P) {
  1/(1+exp(-P))
} 
pred <- link(log.odds) # Transform log-odds into predicted probabilities
pred <- as.vector(pred) 
range(pred) # variation in the predicted probabilities: very little variation.
dev.off()
# Create separation plot to visualize the predictive power of the model
plot_model2 <- separationplot(pred = pred, actual = actual, type = "rect", heading = "Model2: The Parsons Thesis", xlab = "ER Vote Intention", newplot = F, line = T, lwd2 = 0.8, height = 0.5, show.expected = T) 
```

@@

# Model 3: Group Conflict Model (Various theories)
Group conflict theories encompass a variety of theories.  Some emphasize the role of instrumental rationality, arguing that xenophobia results from a contest between immigrants and residents over scarce resources like jobs and welfare benefits. Others emphasize the scapegoating of immigrants as perceived threats to residents' status, power or resources.  In this last model, we use relevant variables representing both the availability of resources like jobs and welfare benefits and the prevalence of immigration: unemployment rates, unemployment benefits, number of asylum seekers, saliance and variance of right-wing issues.

@@

log.odds <- model_3$fitted.values # Create a function with log-odds
# Create link function to transform log-odds into predicted probabilities
link <- function(P) {
  1/(1+exp(-P))
} 
pred <- link(log.odds) # Transform log-odds into predicted probabilities
pred <- as.vector(pred) 
range(pred) # variation in the predicted probabilities: very little variation.
dev.off()
# Create separation plot to visualize the predictive power of the model
plot_model3 <- separationplot(pred = pred, actual = actual, type = "rect", heading = "Model3: The Group Conflict Thesis", xlab = "ER Vote Intention", newplot = F, line = T, lwd2 = 0.8, height = 0.5, show.expected = T) 
```

@@

>>>>

---
title: "Gozde and Liora extension"
author: "Liora and Gozde"
date: "April 27, 2015"
output:
  html_document:
    pandoc_args: [
      "+RTS", "-K64m",
      "-RTS"
    ]
---
# EXTENSION

@@

```{r}
library(separationplot)
library(Hmisc)

@@

log.odds <- model_1$fitted.values # Create a vector with log-odd values
# Create link function to transform log-odds into predicted probabilities
link <- function(P) {
  1/(1+exp(-P))
} 
pred <- link(log.odds) # Transform log-odds into predicted probabilities
pred <- as.vector(pred) 
range(pred) # variation in the predicted probabilities: very little variation.
dev.off()
# Create separation plot to visualize the predictive power of the model
separationplot(pred = pred, actual = actual, type = "rect", heading = "Model1: The Adorno Thesis", xlab = "ER Vote Intention", newplot = F, line = T, lwd2 = 0.8, height = 0.5, show.expected = T) 
```

![Model 1](figures/SP.Model1.png)

@@

# Model 2: Parsons Thesis (Social Disintegration)

Parsons' 1942 theory of social disintegration posits that anomia, a breakdown of social norms, and attendant feelings of anxiety, anger and isolation brings about a longing for strong leadership and rigid ideologies that extreme right parties can provide.  While we do not have measures for the emotions of participants in the studies whose data we use, in our second model we examine the relationship between extreme right voting and the kinds of sentiments about social change that Parsons refers to: satisfaction with democracy and the negative evaluation of the European Union.

@@

log.odds <- model_2$fitted.values # Create a function with log-odds
# Create link function to transform log-odds into predicted probabilities
link <- function(P) {
  1/(1+exp(-P))
} 
pred <- link(log.odds) # Transform log-odds into predicted probabilities
pred <- as.vector(pred) 
range(pred) # variation in the predicted probabilities: very little variation.
dev.off()
# Create separation plot to visualize the predictive power of the model
separationplot(pred = pred, actual = actual, type = "rect", heading = "Model2: The Parsons Thesis", xlab = "ER Vote Intention", newplot = F, line = T, lwd2 = 0.8, height = 0.5, show.expected = T) 
```

![Model 2](figures/SP.model2.png)

@@

# Model 3: Group Conflict Model (Various theories)

Group conflict theories encompass a variety of theories.  Some emphasize the role of instrumental rationality, arguing that xenophobia results from a contest between immigrants and residents over scarce resources like jobs and welfare benefits. Others emphasize the scapegoating of immigrants as perceived threats to residents' status, power or resources.  In this last model, we use relevant variables representing both the availability of resources like jobs and welfare benefits and the prevalence of immigration: unemployment rates, unemployment benefits, number of asylum seekers, saliance and variance of right-wing issues.

@@

log.odds <- model_3$fitted.values # Create a function with log-odds
# Create link function to transform log-odds into predicted probabilities
link <- function(P) {
  1/(1+exp(-P))
} 
pred <- link(log.odds) # Transform log-odds into predicted probabilities
pred <- as.vector(pred) 
range(pred) # variation in the predicted probabilities: very little variation.
dev.off()
# Create separation plot to visualize the predictive power of the model
separationplot(pred = pred, actual = actual, type = "rect", heading = "Model3: The Group Conflict Thesis", xlab = "ER Vote Intention", newplot = F, line = T, lwd2 = 0.8, height = 0.5, show.expected = T) 
```

![Model 3](figures/SP.model3.png)

@@

All Three Models

![Model 1](figures/SP.Model1.png)

![Model 2](figures/SP.model2.png)

![Model 3](figures/SP.model3.png)
